The Local Group in the Cosmic Web

### 2014-08-13 paper/main.tex
punto 2 andrey + revision

@@

@@

These alignments for the LG pairs could be in contradiction with
findings
\citep{2005ApJ...629..219Z,2008MNRAS.390.1133B,2014MNRAS.443.1274L}
that report a universal trend where the eigenvector $\hat{e}_{3}$
(i.e. the filament direction) marks the infall direction for
substructures. The Milky Way satellites are located at high
galactic latitudes, almost perpendicular to the vector pointing
towards the Andromeda Galaxy, which is the direction that we find aligned with
$\hat{e}_3$.

If the alignment we find in this paper holds, this would imply that
infall in the case of the Milky Way is perpendicular to $\hat{e}_3$,
in contradiction to the accretion along filaments. If the universal accretion
along filaments holds, that would imply that that the Andromeda
galaxy is located perpendicular to $\hat{e}_3$, in contradiction with the strong
alignment found in this paper.

@@

Our results also raise the need to observationally constrain
the alignments of LG pairs with their cosmic web environment. To this end
one could use mass reconstructions from large surveys
\citep{2009MNRAS.394..398W,2011MNRAS.417.1303M,2014arXiv1407.3451W,2014arXiv1406.1004N}
or filament finders \citep{2010MNRAS.407.1449G,2011MNRAS.414..350S}
to select a LG sample to quantify the alignments with the filamentary
structure. 
This allows not only a direct quantification of how common are the LG
aligments but also provides a new test of $\Lambda$CDM.

>>>>

In the GS we already see an anti-alignment signature with the third eigenvector,
lower than for RS samples but still significant, this is an expected result,
even for random pairs with separations of the same order of the scale-lenght of 
underlying environment, just because individual pair members are more likely to lie 
following the density distribution. For instance, in a filamentary density distribution, random 
pairs are more likely to lie along the filament; and in walls, random pairs are more likely
to lie in the wall.

@@

We also explored the main orbit differences between the GS and RS  which could be
responsible of this alignment strength feature, and we have that RS samples contraint
the tangential velocity, then pair orbits are more eccentric as we tighten pair
constraints, and for GS sample there is no tangential velocity constraint at all.
Therefore, to study any relation between orbit eccentricity and alignment, we 
computed for each halo pair in all samples, an approximate orbit 
eccentricity assuming a two body orbit with masses set as the virial 
masses and initial conditions given by current velocity vector and separation.
We found that eccentricity is not responsible for this alignement feature by
selecting a subsample of GS having the same eccentricity than 
2$\sigma$-3$\sigma$ samples where we found no increase in the alignment when
compared with the full GS.

@@

These alignments for the LG pairs could be in contradiction with
some findings
\citep{2005ApJ...629..219Z,2008MNRAS.390.1133B,2014MNRAS.443.1274L}
that report a universal trend where the eigenvector $\hat{e}_{3}$
(i.e. the filament direction) marks the infall direction for
substructures. The Milky Way satellites are located at high
galactic latitudes, almost perpendicular to the vector pointing
towards the Andromeda Galaxy, which is the direction that we found aligned with
$\hat{e}_3$.

If the alignment we found in this paper holds, this would imply that
infall in the case of the Milky Way is perpendicular to $\hat{e}_3$,
in contradiction to the accretion along filaments. If the universal accretion
along filaments holds, that would imply that that the Andromeda
galaxy is located perpendicular to $\hat{e}_3$, in contradiction with the strong
alignment found in this paper.

@@

Our results also raise the need to observationally constraint
the alignments of LG pairs with their cosmic web environment. To this end
one could use mass reconstructions from large surveys
\citep{2009MNRAS.394..398W,2011MNRAS.417.1303M,2014arXiv1407.3451W,2014arXiv1406.1004N}
or filament finders \citep{2010MNRAS.407.1449G,2011MNRAS.414..350S}
to select a LG sample to quantify the alignments with the filamentary
structure. 
This allows not only a direct quantification of how common are the LG
aligments but also provides a new test of $\Lambda$CDM.
